Variability analysis 1

### 2022-07-08 experiment-1/analysis/stats/variability.Rmd
correct typos
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# t test
ioi_dyn_tra_t_test <- t.test(Mean ~ Condition, data = ioi_tra_subject[Skill == "dynamics"], paired = TRUE, alternative = "two.sided")
ioi_dyn_tra_t_test

@@

# effect size
wilcoxeff_dyn_tra <- ioi_tra_subject[Skill == "dynamics"] %>% wilcox_effsize(Mean ~ Condition, paired = TRUE)
wilcoxeff_dyn_tra
```

>>>>

# t test
ioi_dyn_tra_ttest <- t.test(Mean ~ Condition, data = ioi_tra_subject[Skill == "dynamics"], paired = TRUE, alternative = "two.sided")
ioi_dyn_tra_ttest

@@

# effect size
coheneff_dyn_tra <- ioi_tra_subject[Skill == "dynamics"] %>% cohens_d(Mean ~ Condition, paired = TRUE)
coheneff_dyn_tra
```
